Comments on Latent Ranking

### 2020-08-31 output_scripts/aug_updates.Rmd
update for cohorts who have a mouse with no starting or being fought

```{r shuffle cohort and stan fit, slow locally}
current_cohort <- 1

@@

fit_cohort_mmhp <- stan("../lib/model3_current.stan", 
                        ## this will need to be updated
                        data = stan_input_lst,
                        warmup = 10, iter = 200, chains = 4, thin=4,
                        control=list(adapt_delta=0.9,max_treedepth=15))

>>>>

```{r shuffle cohort and stan fit, slow locally}
current_cohort <- 8

@@

# fit_cohort_mmhp <- stan("../lib/model3_current.stan", 
#                         ## this will need to be updated
#                         data = stan_input_lst,
#                         warmup = 10, iter = 200, chains = 4, thin=4,
#                         control=list(adapt_delta=0.9,max_treedepth=15))
